Magic-free Code Extraction of Generic Programs and Recursion Schemes in Coq

### 2024-03-18 paper/paper.tex
RelW

\section{Related Work}
%
%\begin{itemize}
%  \item McBride devised a generalisation of Bove and Capretta's general
%recursive function monad~\cite{McBride15, BoveC01}
%  \item Guarded recursion for productive definitions and general recursion
%~\cite{AtkeyM13, PaviottiMB15}
%  \item PACO library~\cite{HurNDV13}
%  \item Sized Types \cite{HughesPS96, abs-1202-3496}
%  \item Copatterns \cite{AbelPTS13, AbelP16}
%  \item Not that related: extraction for mutable arrays~\cite{SAKAGUCHI2020102372}
%        \item Extraction of Distributed Mobile code in Coq~\cite{MiculanP12}.
%\end{itemize}

\subsection{Program Calculation}

@@

\subsection{Termination Checking}

@@

\subsubsection{Sized Types}

@@

\subsubsection{Divide and Conquer Recursion}

>>>>

\section{Related Work}
%
%\begin{itemize}
%  \item McBride devised a generalisation of Bove and Capretta's general
%recursive function monad~\cite{McBride15, BoveC01}
%  \item Guarded recursion for productive definitions and general recursion
%~\cite{AtkeyM13, PaviottiMB15}
%  \item PACO library~\cite{HurNDV13}
%  \item Sized Types \cite{HughesPS96, abs-1202-3496}
%  \item Copatterns \cite{AbelPTS13, AbelP16}
%  \item Not that related: extraction for mutable arrays~\cite{SAKAGUCHI2020102372}
%        \item Extraction of Distributed Mobile code in Coq~\cite{MiculanP12}.
%\end{itemize}
Encoding recursion schemes in Coq is not new. We compare our work with other
encodings of program calculation techniques in Coq (Section~\ref{sec:calccoq}),
recursion schemes in Coq (Sections~\ref{sec:calccoq} and~\ref{sec:reccoq}).
Finally, we compare our encoding of recursion schemes to other forms of
termination checking (Section~\ref{sec:termcheck}, and sized types
(Section~\ref{sec:sizedT}, as a way to guarantee termination of nonstructural
recursion.

\subsection{Program Calculation}\label{sec:calccoq}

@@

\subsubsection{Divide and Conquer Recursion}\label{sec:calccoq}

\subsection{Termination Checking}\label{sec:termcheck}

@@

\subsubsection{Sized Types}\label{sec:sizedT}

@@
